---
title             : "Lab 8 "
shorttitle        : "Running head"

author: 
  - name          : "Vinita Vader, Xiayou Liu, Sarah Donaldson"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Please forward all the queries with regards to this document to any of the three authors.
abstract: |
 This analysis explores the relationship between teacher experience and math scores. 
  
  
  
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "teacher experience, math scores"
wordcount         : ""

bibliography      : ["r-references.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption: "man, fleqn, noextraspace"
header-includes:
  - \raggedbottom
  - \setlength{\parskip}{0pt}
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
library(tidyverse)
library(rio)
library(janitor)
library(tinytex)
library(knitr)
library(psych)
library(here)
```



# Introduction
Here we will explain how we came up with our hypotheses.

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

```{r table, include=FALSE}
star = import(here("data", "star.csv"), setclass = "tbl_df")
  

star_descriptives <- star %>% 
  mutate(tmathss = scale(tmathss), treadss = scale(treadss)) %>%
  group_by(sex, frl) %>%
  summarize(math_mean = mean(tmathss),
            math_sd = sd(tmathss),
            rdg_mean = mean(treadss),
            rdg_sd = sd(treadss))
star_descriptives

```

```{r kable, results="asis"}
kable(star_descriptives,
      col.names = c("sex", "frl", "math_mean", "math_sd", "rdg_mean", "rdg_sd"),
      caption = "Table 1",
      digits = 2)
```
From Table 1, we can see that that overall, girls perform better than boys in both math and reading. Further, boys and girls with free lunch perform below average in math and reading compared to those who are not in the free lunch program. Finally, it appears that an interaction occurs where boys in the free lunch program perform substantially below average.

```{r}


library(ggplot2)
ggplot(star, aes(x = totexp, y = tmathss,)) +
  theme_minimal() +
  geom_point(color = "gray70", alpha = .7) +
  geom_smooth(method = lm, aes(color = frl)) +
  labs(x = "Teacher Experience (years)",
       y = "Total Math Scale Score",
       color = "Lunch status") +
  theme(legend.position = "bottom",
        legend.direction = "horizontal") +
  scale_color_discrete(labels = c("Paid Meals", "Free/Reduced Price Meals"),
                      guide = guide_legend(reverse=TRUE))
  



```



# Discussion

@hurtz2000personality studied how personality affects teacher's math experience. 
Another study found that bhavioral interventions are necessary [@vernon2008behavioral].

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup


